---
title: "Chapter 5: Hypothesis testing"
author: "Mikiko Karasawa"
date: "2020/11/13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "results/",
dev = "png", dpi = 100)
#install.packages("agricolae")
```

---

#### **Exercise1**  
**For the data InsectSpray, make a table for the number of insects for each spray with the mean, median and standard error.**

```{r}
#load and display the structure
data(InsectSprays)
str(InsectSprays)

#make data frame
Spray <- character()
Number_of_insect <-  numeric()
Mean <-  numeric()
Median <-  numeric()
Standard_error <- numeric()

for (i in levels(InsectSprays$spray)) {
  Spray <- c(Spray, paste("Spray", i))
  x <- InsectSprays$count[InsectSprays$spray == i ]
  Number_of_insect <- c(Number_of_insect, sum(x) )
  Mean <- c(Mean, mean(x))
  Median <-  c(Median, median(x))
  Standard_error <- c(Standard_error, sd(x) / sqrt(length(x)))
  }

DF <- data.frame(Spray, Number_of_insect, Mean, Median, Standard_error)

#print the table with caption
knitr::kable(DF, caption = "Table1. Number of insect, Mean, Median and Standard error for each spray") 
```



---

#### **Exercise2**  
**Print a plot to see the differences of counts between sprays. Include a caption explaining the figure. Which type of plot is the one you choose and why?**    

Here, a boxplot is used for comparing the variability of multiple data, because there is only one variables(spray) and  not ordered.
```{r, fig.cap="Figure1. Effectiveness of InsectSprayA,B,C,D,E and F "}
boxplot(count ~ spray, data = InsectSprays, ylab = "Insect count", xlab = "Type of spray", main = "Insect counts for each spray", col = 2:7)
```
other adding figure caption option:  
#mtext("Figure1. Effectiveness of InsectSprayA,B,C,D,E and F ", side = 1, cex = 0.8, line = 4) 

when figure margin is too large:   
#par(mar = c(0,0,2,0)) #adjust margin  
#par(oma = c(3,3,3,2)) #adjust outer margin area  

---

#### **Exercise3**  
**Test for differences between sprays using anova and a posthoc comparison and redo the previous plot including the representation of all posthoc differences.**

```{r}
#ANOVA　　
a1 <- aov(count~spray, data = InsectSprays)
a1
summary(a1)
```


```{r}
#TukeyHSD
TukeyHSD(a1)
```

Between C-A,D-A,E-A,C-B,D-B,E-B,F-C,F-D,F-E are p value < 0.05 and significant different  

```{r}　
#install.packages("agricolae")
library("agricolae")

#HSD test and plot
HT <- HSD.test(a1, "spray")
HT
```
**TukeyHSD()** : Create a set of confidence intervals on the differences between the means of the levels of a factor with the specified family-wise probability of coverage. The intervals are based on the Studentized range statistic, Tukey's ‘Honest Significant Difference’ method.  
**HSD.test()**: Multiple comparisons of treatments by means of Tukey. (α=0.05).  

```{r, fig.cap="Figure2. Effectiveness of InsectSprayA,B,C,D,E and F.Show results with siginifant differences by TukeyHSD test. "}
boxplot(count ~ spray, data = InsectSprays, ylab = "Insect count", xlab = "Type of spray", main = "Insect counts for each spray", col = 2:7)
text(x = 1:6, y = 25, c("a","a","b","b","b","a")) #show groups
```

---

#### **Exercise4**  

**Test for differences between sprays using non-parametric Kruskal-Wallis rank sum test. Again, redo the plot with these results.**


```{r, fig.cap="Figure3. Effectiveness of InsectSprayA,B,C,D,E and F. Show results with siginifant differences by Kruskal-Wallis test. "}
data("InsectSprays")
kw <- kruskal(InsectSprays$count, trt = InsectSprays$spray)
kw
boxplot(count ~ spray, data = InsectSprays, ylab = "Insect count", xlab = "Type of spray", main = "Insect counts for each spray", col = 2:7)
text(x = 1:6, y = 25, c("a","a","c","b","bc","a")) #show groups

```



---

#### **Exercise5**  

**Transform count data using sqrt(counts) and redo the anova, the Tukey posthoc comparison and the plot.**  

```{r}
data("InsectSprays")
SC <- sqrt(InsectSprays$count)   #squire root
a2 <- aov(SC~spray, data = InsectSprays)
#ANOVA
a2
summary(a2)
#Tukey to see significant difference between 2 sprays
TukeyHSD(a2)

#HSDtest for grouping
HSDtest <- HSD.test(a2, "spray")
HSDtest
```

```{r, fig.cap="Figure4. Effectiveness of InsectSprayA,B,C,D,E and F.Show results with siginifant differences by TukeyHSD test. "}
#make boxplot
boxplot(SC ~ spray, data = InsectSprays, ylab = "Insect count", xlab = "Type of spray", main = "Insect counts for each spray (Square root)", col = 2:7)
text(x = 1:6, y = 5, c("a","a","c","b","bc","a")) #show groups
```

---

#### **Exercise6**  　
**Test for normality of residuals for the two performed anova analyses of points 4 and 6 using shapiro.test() and use plot the anova to see the qqplots and compare them.**

```{r}
#shapiro test for direct ANOVA
a1r <- a1$residuals
shapiro.test(a1r)
```
p-value = 0.02226, not normal distribution  

```{r}
#shapirotest for square root transformed ANOVA 
a2r <- a2$residuals
shapiro.test(a2r)
```
p-value = 0.6814, normal distribution  

```{r, fig.cap= "Figure5. QQ plot for direct ANOVA" }
#use plot the anova to see the qqplots and compare them
qqnorm(a1r, main = "QQ plot for direct ANOVA")
qqline(a1r)
```

```{r, fig.cap="Figure6. QQ plot for square root transformed ANOVA"}
qqnorm(a2r, main = "QQ plot for square root transformed ANOVA")
qqline(a2r)
```


From QQ plot, the square root transformed data seems to follow a normal distribution.


#### **Exercise7**  　
**(1)Which of the previous analysis is the adequate in this case? Why? (2)Is there any difference in the results between the square root transformed ANOVA and the Kruskal-Wallis analyses? (3)Is there any difference in the results between the direct ANOVA and the square root transformed ANOVA? Which ones?**

(1)For direct ANOVA data, p-value is 0.02226 which is not normal distribution. For square root transformed data, p-value = 0.6814 and follow normal distribution. Therefore, the square data is adequate for the analysis.  

(2)There is no difference between the square root transformed ANOVA and the Kruskal-Wallis analyses.  

(3)There are differences between the direct ANOVA and the square root transformed ANOVA. In spray C,D,E, there are difference.



